%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-owner \& Chief Technical Officer} % Job title
    {JMKRIDE USA} % Organization
    {San Diego, CA} % Location
    {Sep. 2019 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          \textbf{Stocktracker}: Built and deployed an internal inventory management website 
          \newline\entrystackstyle{v1: Javascript, Python, MySQL, v2: React, Node.js, MongoDB}
          \begin{itemize}[leftmargin=0.5cm]
            \item{Fully dynamic inventory structure of parts, categories, category sets}
            \item{Multiple inventories, multiple users, and user-attributed logs of every action}
            \item{Historic part quantity graphs for visualizing inventory trends}
          \end{itemize}
        }
        \item {
          \textbf{Ambassador Portal}: Built and deployed a customer-facing
          brand ambassador/affiliate portal website.
          \newline\entrystackstyle{React, React Native, React Query, Node.js, MongoDB}
        }
        \item{
          \textbf{Freeskater Finder}: Built and deployed a customer-facing web
          app. Users place their pin on the map and connect with other
          freeskaters.
          \newline\entrystackstyle{React, Google Maps Javascript API, Material UI, Node.js, MongoDB}
          \begin{itemize}[leftmargin=0.5cm]
            \item{
              Users create an account, input a bio, profile picture, and their
              social media links.
            }
            \item{
              Users configure their visibility and privacy, controlling whether
              friend requests are required.
            }
          \end{itemize}
        }
        \item{
          \textbf{usa.jmkride.com}
          Installed and customized the store Shopify theme
          \entrystackstyle{Liquid, Shopify API, Shopify Themes}
        }
        \item{
          Built and deployed a custom Shopify app allowing automatic referal
          code usage recording from our Shopify shop
          \newline\entrystackstyle{Heroku, Shopify API, GraphQL, Javascript}
        }
        \item{
          \textbf{jmkride.com}
          Designed and customized the international website
          \entrystackstyle{Wix, Javascript}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Production Engineer} % Job title
    {Facebook} % Organization
    {Menlo Park, California} % Location
    {Sep. 2017 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Maintain the performance and reliability of hundreds of thousands
          of servers running several cache services including TAO, Facebook's
          social graph cache, backed by the world's largest MySQL deployment.
        }
        \item {
          Designed, developed, and deployed new internal systems including a
          load-test service to detect performance regressions, and a
          disaster-event simulator to test reliability during unplanned
          unavailability events like network cuts or DC power loss.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
%  \cventry
%    {Production Engineering Intern} % Job title
%    {Facebook} % Organization
%    {Menlo Park, California} % Location
%    {June. 2016 - Aug. 2016} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {
%          Designed and developed a performance testing system for Linux kernel
%          system modifications for the Facebook ads production environment.
%        }
%      \end{cvitems}
%    }
%
%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {ViaSat Inc.} % Organization
    {Carlsbad, California} % Location
    {May. 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a highly modular cloud-based testing infrastructure for Viasat's next generation core switch}
        \item {Wrote Ansible playbooks to deploy the application as a fully scalable VM cluster to the OpenStack cloud}
        \item {
          Final product was phased into use by the ViaSat Satallite Applications
          team before the conclusion of the internship, and is currently seeing
          daily use in testing their development environments. 
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student System Administrator} % Job title
    {Harvey Mudd College} % Organization
    {Claremont, California} % Location
    {May. 2014 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Administer of numerous Linux servers for use by the Harvey Mudd Computer Science Department and its students}
        \item {Servers provide services including Subversion, Git, Trac, NFS, LDAP, DNS, and Apache}
        \item {
          Built two high performance VM hosting servers using Gentoo Linux and
          the KVM/QEMU hypervisor to host remote linux servers to students of
          the system administration class.
        }
        \item{Co-taught aforementioned system administration class for the fall and spring semesters 2015}
        \item{Awarded the JArthur award in 2015 for exceptional performance}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
